### 2024-06-14 conteudo/tool/architecture.tex
Add more work, 14/06

\subsection{Tool architecture}
\label{subsec:architecture}

@@

\subsubsection{Input codebase}

@@

\subsubsection{Function Parser}

The Function Parser receives the input codebase and transforms it into the temporary codebase. The Function Parser iterates through
every source code file from the programming language it support and use a specific programming languague's function 
extractor to extract
every function in the file, for each function extracted we create a new source code file and a metadata file in the temporary codebase
which is represented by the pair \textbf{<source code file, function extracted>}, which represents the source code file the 
function is extracted from and the 
proper function. The new source code file only contains the source code from the function it represents, while the metadata file 
contains extra relevant information such as function name, the line the function it began to be declared in the original souce code 
file and the line the function's body ends in the original source code file. The programming language we support at the moment 
is C and Java. Can be found a example of a transform of a source code in the (CRIAR UM APENDICE E COLOCAR AQUI).

@@

\subsubsection{Code Duplication Finder}

\subsubsection{Code Duplication Database}

\subsubsection{Setup step}

\subsubsection{Query Responder step}

>>>>

\section{Tool architecture}
\label{subsec:architecture}

@@

\subsection{Input codebase}

@@

\subsection{Function Parser}

The Function Parser receives the input codebase and transforms it into the temporary codebase. The Function Parser iterates through
every source code file from the programming language it support and use a specific programming languague's function 
extractor to extract
every function in the file, for each function extracted we create a new source code file and a metadata file in the temporary codebase
which is represented by the pair \textbf{<source code file, function extracted>}, which represents the source code file the 
function is extracted from and the 
proper function. The new source code file only contains the source code from the function it represents, while the metadata file 
contains extra relevant information such as function name, the line the function it began to be declared in the original souce code 
file and the line the function's body ends in the original source code file. The programming language we support at the moment 
is C and Java. Can be found a example of a transform of a source code in the (CREATE APENDIX AND ADD HERE).

@@

\subsection{Code Duplication Finder}

The Code Duplication Finder iterates through every pair of source code files in the temporary codebase, which in this context represents
functions of the input codebase, and for every pair of files, we execute a code duplication detection method that computes a metric
that measures of how similar the pair of files are, which we call similarity. Finally, if the similarity is greater of equal then the
minimum similarity threshold (a parameter passed by the user when it executes the Setup step), we store this pair of files along with
it similarity in the Code Duplication Database.

For the code duplication detection method, we visualize the source code files as texts and execute the TF-IDF vector embedding method
implemented by the Gensim library \citep{gensim} and compute the cosine similarity as the similarity metric. We chose this method 
given the alegated Gensim statements about itself performance, being a programming language independent method and the nonnecessity of 
compilable code, which is expected to happen in the temporary codebase as it not stores complete code artifacts. Platis implemented
this code cuplication detection method and distributed it to the public with a MIT license \citep{platistool} \citep{mitlicense}, 
we utilize his implementation as it has some nice to have components such as removing code comments, we do the appropriated changes
in the input and output of his implementation to respect the expected format of our tool. 
It is feasible to change the duplication detection method in a manner similar to what we did with Platis's implementation.

\subsection{Code Duplication Database}

\subsection{Setup step}

\subsection{Query Responder step}
